\section{Stable Rank}

\begin{definition}
  Let $A$ be a unital C*-algebra. For each $n \in \N$, define
  \begin{align*}
    {\rm Lg}_n(A) := \{(a_1,a_2, \ldots, a_n) \in A^n| Aa_1 + Aa_2 + \cdots + Aa_n =A\}.
  \end{align*}
  Then the stable rank of $A$ is defined to be the value
  \begin{align*}
    {\rm min}\{n \in \N | {\rm Lg}_n(A)\, is\, norm\, dense\, in\, A\}.
  \end{align*}
\end{definition}

\begin{proposition}[\cite{rieffel1983dimension}, Proposition 3.1]
  A unital C*-algebra has stable rank one if and only if the set of invertible elements of $A$ is norm dense in $A$.
\end{proposition}

\begin{definition}
  Let $A$ be a C*-algebra. Denoted by $\rm{ZD}(A)$ the set of two-sided zero divisor in $A$, i.e.,
  the set of elements $x$ in $A$ for which $ax=xb=0$ for some non-zero elements $a$ and $b$ in $A$.
\end{definition}

\begin{proposition}[\cite{rordam1991structure}, proposition 3.2]
  For each unital C*-algebra $A$, $\overline{{\rm ZD}}(A)$ consists precisely of all elements $x$ in $A$ that are not one-sided invertible. 
\end{proposition}

\begin{proof}
  Let $X$ be a set of all  elements $x$ in $A$ that are not one-sided invertible.
  At first, we show that ${\rm ZD}(A) \subset X$.
  Let $x \in {\rm ZD}(A)$.
  Since $\mathcal{R}(x) \neq H$ and $\ker(x) \neq H$, $x \in X$.
  We show that $X$ is closed.
  Suppose $a, x \in A$ and $x_n \in X$ s.t. $ax=1$ and $x_n \rightarrow x$.
  There exists $n$ s.t. $\|ax_n -1\| < 1$.
  So, $ax_n \in {\rm GL}(A)$, this is contradiction.
  So, we suffices to show that $\overline{{\rm ZD}}(A) \supset X$. Let $x \in X$ and $\varepsilon > 0$.
  Then, neither $|x|$ nor $|x^*|$ is invertible
  (since if $|x|$ is invertible, $x^*x = |x|^2$ is invertible).
  Suppose $f_\varepsilon ,g : \R_+ \rightarrow \R_+$ be continuous funsctions s.t.
  \begin{align*}
    f(x) := \left\{\begin{gathered} 0\;\;  (x \in [0,\varepsilon]\\
    x-\varepsilon\;\; (x \in [\varepsilon, \infty) \end{gathered} \right.,\,
    g:\left\{\begin{gathered} g(0) = 1\\
    {\rm supp}(g) \subset [0,\varepsilon]. \end{gathered} \right.
  \end{align*}
  Let $x = v|x|$ by polar decomposition.
  Let $a := g(|x^*|)$, $b := g(|x|)$ and $x_\varepsilon := v f_\varepsilon (|x|)$.
  Then, $ax_\varepsilon = 0 = x_\varepsilon b$.
  Since $0 \in \sigma(|x)$ and $0 \in \sigma(|x^*|)$,
  $a,b \neq 0$.
  So, $x_\varepsilon \in {\rm ZD}(A))$.
  Since $\|x - x_\varepsilon\| \leq \varepsilon$, $x \in \overline{{\rm ZD}}(A)$.
\end{proof}
