
\section{Takesaki}
\subsection{Egorov and Lusin}
\begin{theorem}[Egorov's lemma]
Let be $(\Omega$, $\mathcal{F}$, $\mu)$ a finite measure space. 
Let be ${\{ f_n \}}_{n \in \mathbb{N}}$ and $f$ measurable functions.
Suppose ${\{ f_n \}}_{n \in \mathbb{N}} \rightarrow f$ a.e. 
Then, for each $\epsilon > 0$, There exists $\mathcal{F} \subset A$ s.t. $\mu (\Omega - A) < \epsilon$ and ${\{ f_n \}}_{n \in \mathbb{N}}$ convergent $f$ uniformly  on $A$.
\end{theorem}

\begin{theorem}[Lusin's theorem]
Same assumption.
Then, for each $\epsilon > 0$, There exists $\mathcal{F} \subset A$ s.t. $\mu (\Omega - A) < \epsilon$ and $f$ is continuous on$A$.
\end{theorem}

\begin{theorem}[noncommutative Egorov's theorem]
Let $(M,H)$ be von Neumann algebra and $A \subset M$ be a bounded subset. 
Suppose any $a \in {\overline{A}}^{s}$, any $\varphi \in M_{*,+}$, any $e \in P(M)$, any $\epsilon > 0$.\, 
Then, there exists $e_0 \in P(M)$ s.t. $e_0 \leq e$ and a sequence ${\{ a_n \}}_{n \in \mathbb{N}} \subset A$ s.t. $\lim_{n \to \infty} ||(a-a_n)e_0|| = 0$,\, $\varphi (e-e_0) < \epsilon$.
\end{theorem}

\begin{theorem}[noncommutative Lusin's theorem]
Let A be a C*-algebra. Suppose $M={\overline{A}}^{s}$. 
Suppose $0 \neq \varphi \in M_{*,+}$, $0 \neq e \in P(M)$, $\epsilon$, $\delta > 0$.
\begin{itemize}
\item For each $a \in M$,there exists $e \geq e_0 \in P(M)$ and $a_0 \in A$ s.t. $a e_0=a_0 e_0$ and $||a_0|| \leq (1+\delta)||a e_0||$.
\item For each $a \in M_{sa}$, there exsists $e \geq e_0 \in P(M)$ and $a_0 \in A_{sa}$ s.t. $a e_0=a_0 e_0$,\, $||a_0|| \leq \min \{2(1+\delta)||a e_0||,||a||+\delta \}$.
\item Let $1 \in A$. For each $a \in \mathcal{U}(M)$, there exists $e \geq e_0 \in P(M)$ and $a_0 \in \mathcal{U}(A)$ s.t. $a e_0=a_0 e_0$, $||a_0 - 1|| \leq ||a-1|| + \delta$.
\end{itemize}
\end{theorem}

If $\varphi = {\rm Tr}$, the following theorem is followed.

\begin{theorem}[Transitivity theorem]
Let A be a irredusible C*-algebra on H. For eqch finite projection $e \in P(M)$, $Ae=B(H)e$.
\end{theorem}

\begin{table}[h]
  \begin{tabular}{|c|c|}\hline
    $\Omega$ & M \\ \hline
    $\mathcal{F}$ & P(M)  \\ \hline
    $\mu$ &$\varphi$ ( $\in M_{*,+}$) \\ \hline
    measurable function & M \\ \hline
    $f:\Omega \rightarrow \C$ & $a:M \rightarrow M$ \\ \hline
  \end{tabular}
\end{table}

\subsection{universal representation}
\begin{theorem}
Let $A$ be a C*-algebra and ($\pi$,$H$) be a representation of $A$. 
\begin{figure}[h]
$$
\xymatrix{
A \ar[rr]^{\pi}  \ar[d]^{\iota}&  & {\pi(A)}'' \\
A^{**} \ar[urr]^{\tilde{\pi}} 
}
$$
\end{figure}
\end{theorem}

\subsection{Polar decomposition}
\begin{theorem}
closed left invariant subspace $\longleftrightarrow$ $\sigma$-w closed right ideal \\
$M_{*} \supset V = J^{0} = M_{*} e \, \longleftrightarrow \, M \supset J = V^{0} =(1-e)M$
\end{theorem}

\begin{example}
  $l^2(\Z)$
\end{example}
  
\begin{theorem}
Let $X$ and  $Y$ be Banach sp.s. Let $B_X$ be a unit open ball. If $T(B_X)=B_Y$,then injective.
\end{theorem}

\begin{theorem}
  Let $A < B$ be C*-algebras. 
  Let $E:B \rightarrow A$ be a surjective map, which statisfies $E(a)=a \,(a \in A)$,\, $||E(x)|| \leq ||x||$.
  Then, it is conditional expectation. 
\begin{itemize}
\item $E(x^{*}x) \geq 0 \,(x \in B)$
\item $E(axb)=aE(x)b\,(a,b \in A,\, x \in B)$
\item ${E(x)^{*}E(x)} \leq E(x^{*}x)$
\end{itemize}
\end{theorem}

\begin{theorem}
  $\omega$ is normal $\Leftrightarrow$ for all $\{ p_n \} \subset P(M)$, $\omega(\sum p_n) = \sum \omega (p_n)$.
\end{theorem}
  
\begin{theorem}
  $\varphi \in M_{*}$. There exsit unique $v \in M$ and $\omega \in M_{*,+}$ s.t. $\varphi = v \omega$, $v^{*}v = s(\omega) = s_r(\varphi)$, $vv^{*} = s_l(\varphi)$.
\end{theorem}




\begin{definition}
Let $(M_i , {\tau}_i)$ be tracial von Neumann algebras. \\
$(M,\tau)$ is called free product von Neumann algebra, if it satisfies the following properties. \\
${\varphi}_i : M_i \rightarrow M$ are hom and ${\tau}_i = {\tau} \circ {\varphi}_i$, 
${\varphi}_i (M_i)$ are free with respect to $/tau$, and generates $M$. \\
von Neumann subalgebras$M_i$ of von Neumann algebra$M$ is free with respect to faithful normal state,
if for each $x_i \in M_{k_i}$with\, $k_1 \neq \cdots  \neq k_n$,\, $\tau (x_i) = 0$, $\tau (x_1 \cdots x_n) = 0$.
\end{definition}



\begin{theorem}
Let $(M_i , {\tau}_i)$ be tracial von Neumann algebras. 
Let $(M,\tau)$ be its free product von Neumann algebra. 
Let $Q$ be deffuse von Neumann subalgebra of $M_1$. 
Then, $Q' \cap M \subset M_1$. 
Specially, $Z(M) \subset Z(M_1)$,therefore if  $M_1$ is a ${I\hspace{-.1em}I}_1$factor , so is $M$. 
\end{theorem}

\begin{proof}
A masa of tracial deffuse von Neumann algebra is deffuse, since conditinal expectation. \\
separable abelian diffuse von Neumann algebra is isomorphic to $L^{\infty}([0,1],\mu)$($\mu$:Leb), 
and faithful state is given by integration, so $u_n = exp(2 \pi i n t)$ is $\tau(u_n) = 0$, and $w-\lim u_n = 0$(Riemann-Lebesgue). \\

It suffices to show $x \in \ker ({\tau}_1)$ is $0$. \\
Since $E_{M_1}$ is faithful, it suffices to show $E_{M_1} (x*x) = 0$. \\
For each $x,y \in M$with$E_{M_1} (x) = 0$ and $E_{M_2} (y) = 0$, it suffices to show $\lim ||E_{M_1} (x u_n y) ||=0$.\\
Since $ker({\tau}_1)$ideal, $E_{M_1} (x u_n y) = {\tau}_1 (b u_n d) x_1 a c y_1$. Because $b,d$ are $ker({\tau}_1) \cup \{ 1 \}$, QED.
\end{proof}

\begin{theorem}
Let $(M,\tau)$ be a tracial von Neumann algbera, $e_B \in P(L^2(M))$ be a projection onto $L^2(B)$. Suppose $B=\<B,e_B\>$.\\
\begin{itemize}
\item $B = M \cap \{e_B \}'$;
\end{itemize}

\end{theorem}

\subsection{amplification}

\begin{theorem}
  Let $\{M_1,H_1\}$and $\{M_2, H_2\}$ be vN algebras. \\
  If $\pi$ is a normal hom of $M_1$ onto $M_2$, then there exists a Hilbert sp. $K$, $e' \in \mathcal{P}(M_1'\otimes B(K))$and isometry $U$ of $e'(H_1\otimes K)$onto $H_2$s.t. $\pi(x)= U(x\otimes 1_K)_{e'}U^*  (x \in M_1)$.
  \[
  \xymatrix{
    e'(H_1\otimes K) \ar[r]^{(x\otimes 1_K)_{e'}} \ar[d]^U & e'(H_1\otimes K) \ar[d]^U \\
    H_2 \ar[r]^{\pi(x)}& H_2
  }
  \]
\end{theorem}

\begin{proof}
  Let $\{\xi_i\} \subset H_2$ be a maximal family s.t. $H_{2,i}[\pi(M_1)\xi_i]$ are mutually orthogonal.
  Then, $H_2 = \oplus_i H_{2,i}$.\\
  Let $K_i$ be a separable infinite dimensional Hilbert sp, $K$ be a $\otimes K_i$and $\pi_1$ be a amplification of $M_1$.
  Since ${}^t\pi(\omega_{\xi_i}) \in M_*^+$, there exists $\zeta_i \in H \otimes K_i$ s.t. ${}^t\pi_1(\omega_{\zeta_i})={}^t\pi(\omega_{\xi_i})$.\\
  Let $e'$ be a projection of $H\otimes K$ onto $\otimes_i [\pi_1(M_1)\zeta_i]$, which bvelongs to ${\pi_1(M_1)}'$.\\
  Let isometry $U_i$ be a extention of $[\pi_1(M_1)\zeta_i]$ onto $H_i$ and $U = \oplus_i U_i$.
\end{proof}

\subsection{semifinite}
\begin{proposition}
  Let $M$ be a von Neumann algebra with faithful normal semifinite trace. If $N < M$ is a von Neumann subalgebra and $\tau|_N$ is semifinite, there exists faithful normal conditional expectation $E$ of $M$ onto $N$ s.t. $\tau = \tau \circ E$.
\end{proposition}

